Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

Another closely related query is the {\em reverse-containment query}, which, given an interval $q = [z_1, z_2]$, finds all the intervals of $S$ that contain $q$ (rather than ``being contained by $q$''). Again, we can store $S$ in a PST using $O(|S|)$ space such that any such query can be answered in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. In general, an interval $[z_1, z_2]$ contains another $[x, y]$ if and only if the point $(x, y)$ is covered by the 3-sided rectangle $(-\infty, z_1] \times [z_2, \infty)$. Thus, we create from $S$ a point set $P = \set{(x, y) \mid [x, y] \in S}$ and store $P$ in a PST. Given an interval $q = [z_1, z_2]$, we use the PST to find all the points in $P$ covered by $(-\infty, z_1] \times [z_2, \infty)$ and, for each such point $(x, y)$, report $[x, y]$.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$.} Sort all the rectangles $r \in R$ in ascending order of $\xright(r)$ (namely, the x-coordinate of the right edge of $r$). To each $r \in R$, we assign an ID $i \in [R]$ if $r$ is at the $i$-th position of the sorted list.

@@

Next, we aim to produce, for each pair $(h, r) \in H \times r$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.

@@

\section{Completing the Proof of Lemma~\ref{lmm:hv}} \label{app:hv}

@@

>>>>

Another closely related query is the {\em reverse-containment query}, which, given an interval $q = [z_1, z_2]$, finds all the intervals of $S$ that contain $q$ (rather than ``being contained by $q$''). Again, we can store $S$ in a PST using $O(|S|)$ space such that any such query can be answered in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. In general, an interval $[x, y]$ contains another $[z_1, z_2]$ if and only if the point $(x, y)$ is covered by the 3-sided rectangle $(-\infty, z_1] \times [z_2, \infty)$. Thus, we create from $S$ a point set $P = \set{(x, y) \mid [x, y] \in S}$ and store $P$ in a PST. Given an interval $q = [z_1, z_2]$, we use the PST to find all the points in $P$ covered by $(-\infty, z_1] \times [z_2, \infty)$ and, for each such point $(x, y)$, report $[x, y]$.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$.} Sort all the rectangles $r \in R$ in ascending order of $\xright(r)$ (namely, the x-coordinate of the right edge of $r$). To each $r \in R$, we assign an ID $i \in [|R|]$ if $r$ is at the $i$-th position of the sorted list.

@@

Next, we aim to produce, for each pair $(h, r) \in H \times r$ such that $r$ crosses $h$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.

@@

\section{Supplementary Proofs for Section~\ref{sec:hv:type1}} \label{app:hv:type1}

@@

\section{Supplementary Proofs for Section~\ref{sec:hv:type2}} \label{app:hv:type2}
